SU($n$) spin models near the Heisenberg critical point

### 2020-03-25 collective_sun/sun_perturbation.tex
fix typo in notes

In order to induce non-trivial dynamics for initially PS states
$\ket\psi\in\M_0$, which are otherwise stationary eigenstates of the
interaction Hamiltonian $H_0$ in \eqref{eq:H_0}, we will add to the
Hamiltonian an operator $\hat\O$ of the general form
\begin{align}
  \hat\O \equiv \sum_{\p{X,\m w}\in\O} X_{\m w},
  &&
  X_{\m w} \f1M! \equiv \sum_{k\in\D_N\p{M}} w_k X_k,
  \label{eq:pert}
\end{align}
where $\hat\O$ is constructed from the set $\O\equiv\set{\p{X,\m w}}$
of $M$-spin operators $X$ together with dimension-$M$ (i.e.~$M$-index)
tensors $\m w$; $k=\p{k_1,k_2,\cdots,k_M}$ is a list of of $M$ spins
that $X_k$ acts on; $w_k$ is a scalar entry of $\m w$; and
\begin{align}
  \D_N\p{M} \equiv
  \set{ k \in \ZZ_N^M: \t{all entries of}~k~\t{are distinct} },
  \label{eq:off_diags}
\end{align}
is the strictly off-diagonal part of $\ZZ_N^M$.  The factor of $1/M!$
is included in \eqref{eq:pert} by convention to average over the $M!$
terms addressing any given set of spins.  Due to the permutational
symmetry enforced by the interaction Hamiltonian $H_0$, we will find
it convenient to decompose $\D_N\p{M}=\pi\p{M}\times\C_N\p{M}$, where
$\pi\p{M}$ is the permutation group of $\ZZ_M$, and
\begin{align}
  \C_N\p{M} \equiv \set{ k \subset \ZZ_N: \abs{k} = M },
  \label{eq:choices}
\end{align}
is the set of subsets (``choices'') of $M$ elements from $\ZZ_N$.  We
can then expand
\begin{align}
  X_{\m w} = \f1{M!} \sum_{\sigma\in\pi\p{M}} \sum_{k\in\C_N\p{M}}
  w_{\sigma\p{k}} X_{\sigma\p{k}}.
\end{align}
For simplicity, we will assume throughout this work that $\hat\O$ is
homogeneous in the sense that $M$ is the same for all
$\p{X,\m w}\in\O$, with the understanding that a generalization to
inhomogeneous operators $\hat\O$ is straightforward.

@@

In this section, we simplify the products of the form
$H_0X_{\m w}\ket\psi$ to arrive at the expansion in
\eqref{eq:diagnosis}, which defines conditions under which a
multi-body perturbation $X_{\m w_\Delta}$ generates eigenstates of the
SU($n$)-symmetric interaction Hamiltonian $H_0$ in \eqref{eq:H_0} when
acting on a permutationally symmetric state $\ket\psi\in\M_0$.  Here
$X_{\m w}$ is an $M$-body perturbation defined by
\begin{align}
  X_{\m w}
  \equiv \sum_{k\in\D_N\p{M}} w_k X_k
  = \sum_{k\in\C_N\p{M}} \sum_{\sigma\in\pi\p{M}}
  w_{\sigma\p{k}} X_{\sigma\p{k}},
\end{align}
where $X$ is an $M$-spin operator; $k\equiv\p{k_1,k_2,\cdots,k_M}$ is
a list of $M$ spins that $X_k$ acts on; $\m w$ is a dimension-$M$
(i.e.~$M$-index) tensor with scalar entries $w_k$; $\D_N\p{M}$ is the
strictly off-diagonal part of $\ZZ_N^M$, defined in
\eqref{eq:off_diags}; $\C_N\p{M}$ is the set of all choices of $M$
elements from $\ZZ_N$, defined in \eqref{eq:choices}; and $\pi\p{M}$
is the permutation group of $\ZZ_M$.

>>>>

In order to induce non-trivial dynamics for initially PS states
$\ket\psi\in\M_0$, which are otherwise stationary eigenstates of the
interaction Hamiltonian $H_0$ in \eqref{eq:H_0}, we will add to the
Hamiltonian an operator $\hat\O$ of the general form
\begin{align}
  \hat\O \equiv \sum_{\p{X,\m w}\in\O} X_{\m w},
  &&
  X_{\m w} \equiv \f1{M!} \sum_{k\in\D_N\p{M}} w_k X_k,
  \label{eq:pert}
\end{align}
where $\hat\O$ is constructed from the set $\O\equiv\set{\p{X,\m w}}$
of $M$-spin operators $X$ together with dimension-$M$ (i.e.~$M$-index)
tensors $\m w$; $k=\p{k_1,k_2,\cdots,k_M}$ is a list of of $M$ spins
that $X_k$ acts on; $w_k$ is a scalar entry of $\m w$; and
\begin{align}
  \D_N\p{M} \equiv
  \set{ k \in \ZZ_N^M: \t{all entries of}~k~\t{are distinct} },
  \label{eq:off_diags}
\end{align}
is the strictly off-diagonal part of $\ZZ_N^M$.  The factor of $1/M!$
is included in \eqref{eq:pert} by convention to average over the $M!$
terms addressing any given set of spins.  Due to the permutational
symmetry enforced by the interaction Hamiltonian $H_0$, we will find
it convenient to decompose $\D_N\p{M}=\pi\p{M}\times\C_N\p{M}$, where
$\pi\p{M}$ is the permutation group of $\ZZ_M$, and
\begin{align}
  \C_N\p{M} \equiv \set{ k \subset \ZZ_N: \abs{k} = M },
  \label{eq:choices}
\end{align}
is the set of subsets (``choices'') of $M$ elements from $\ZZ_N$.  We
can then expand
\begin{align}
  X_{\m w} = \f1{M!} \sum_{\sigma\in\pi\p{M}} \sum_{k\in\C_N\p{M}}
  w_{\sigma\p{k}} X_{\sigma\p{k}}.
\end{align}
For simplicity, we will assume throughout this work that $\hat\O$ is
homogeneous in the sense that $M$ is the same for all
$\p{X,\m w}\in\O$, with the understanding that a generalization to
inhomogeneous operators $\hat\O$ is straightforward.

@@

In this section, we simplify the products of the form
$H_0X_{\m w}\ket\psi$ to arrive at the expansion in
\eqref{eq:diagnosis}, which defines conditions under which a
multi-body perturbation $X_{\m w_\Delta}$ generates eigenstates of the
SU($n$)-symmetric interaction Hamiltonian $H_0$ in \eqref{eq:H_0} when
acting on a permutationally symmetric state $\ket\psi\in\M_0$.  Here
$X_{\m w}$ is an $M$-body perturbation defined by
\begin{align}
  X_{\m w}
  \equiv \f1{M!} \sum_{k\in\D_N\p{M}} w_k X_k
  = \f1{M!} \sum_{\sigma\in\pi\p{M}} \sum_{k\in\C_N\p{M}}
  w_{\sigma\p{k}} X_{\sigma\p{k}},
\end{align}
where $X$ is an $M$-spin operator; $k\equiv\p{k_1,k_2,\cdots,k_M}$ is
a list of $M$ spins that $X_k$ acts on; $\m w$ is a dimension-$M$
(i.e.~$M$-index) tensor with scalar entries $w_k$; $\D_N\p{M}$ is the
strictly off-diagonal part of $\ZZ_N^M$, defined in
\eqref{eq:off_diags}; $\pi\p{M}$ is the permutation group of $\ZZ_M$;
and $\C_N\p{M}$ is the set of subsets (``choices'') of $M$ elements
from $\ZZ_N$, defined in \eqref{eq:choices}.
